---
author: Daniel Slutsky
title: Data scientist, software developer
format:
  classic-cv-pdf: default
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Community organizer at Scicloj
    right: github.com/daslu
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
   
  tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
  res <- paste0(res, "{",tbl[[details]],"}")
  
  cat(res, sep = "\n")
}
```

# Summary

A Mathematician and software engineer. Organizing [Scicloj](https://scicloj.github.io/), the group building Clojure's data science stack. 

# Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
  ~role, ~institution, ~dates, ~tasks,
  #
  "Open-source developer and organizer", "Scicloj", "2019-persent",
  c("Co-maintaining open-source projects. Especially: Kindly, Clay, Notespace, ClojisR, and the Scicloj website.",
    "Running dev groups, study groups, and workshops; mentoring newcomers."),
  #
  "Data scientist, backend engineer", "Madlan / Localize.city", "2014-2023",
  c("Took part in the startup from early stages; recruited and mentored team members.",
    "Worked on data problems in diverse fields including urban spatio-temporal modeling, real-estate pricing, NLP, and recommendation systems. Built data analytics tooling and infrastructure.",
    "Used diverse technologies (Clojure, Java, R, Python, PyTorch, Tensorflow, Stan, PyMC, SQL, QGIS, etc.)."),
  #
  "Machine learning researcher and engineer", "Katros (fincance-related startup)", "2012-2014",
  c("First employee, involved in critical tasks at the team.",
    "Conducted various research projects, mostly time series analysis and machine learning.",
    "Designed and developed a machine learning engineering platform in Clojure."),
  #
  "Mathematician", "Clal Finance", "2010-2011",
  c("Responsible for research projects analyzing financial time series"),
  #
  "Algorithms researcher", "Taboola", "2007-2010",
  c("Member of the founding team.",
    "Developed recommendation systems using NLP, collaborative filtering, and machine learning.")) |>
  cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
  ~degree, ~uni, ~dates, ~details,
  "Yoga teacher training", "Studio Naim", "2018-2019",
  "",
  "M.A. in Sociology", "Tel Aviv University", "2010-2014",
  "",
  "M.Sc. in Math (w. highest honor)", "Tel Aviv University", "2001-2006", 
c("Thesis: Restrictions for Thin Young Diagrams (in the fields of representation theory and noncommutative probability)"),
) |>
  cvevents(when = "dates", what = "degree", where = "uni", details = "details")
```

# Public activity

 

```{r}
#| label: public activity
#| output: asis
tibble::tribble(
  ~role, ~org, ~dates, ~details,
  "Community organizer and team coordinator", "various local movements for social action", "2008-2018",
  "") |>
  cvevents(when = "dates", what = "role", where = "org", details = "details")
```


# Technical Skills
$*$ Sound background in math, particularly probability theory & stochastic processes.

$*$ Time series analysis, spatial analysis, Bayesian methods, random simulations,
machine learning, data visualization, recommendation systems, GIS.

$*$ Clojure, R, Python, C, Java; Tensorflow, PyTorch, Tensorflow Probability, Stan, PyMC; spaCy; Clojurescript, Javascript; Linux shell; DVC; Docker; PostgreSQL; QGIS, etc.

$*$ Teaching and mentoring in diverse topics.
